### 2015-11-11 ResearchStatement/main.tex
Minor edits from Bill

Working with a chemist, we set out to
design better OLED molecules, which underly modern electronics displays.
Given a molecule, its possible to calculate its phosphorescence when excited. However,
there is no direct method for finding molecules which maximize this property.
By applying P3 and other generic optimization methods we found some interesting
molecules for future analysis.

@@

A challenging task in machine learning is the training of large scale neural networks.
I have recently been in collaboration with an evolutionary biologist
who studies natural learning to develop better methods for training artificial brains.

>>>>

Working with a chemist, we set out to
design better OLED molecules, which underly modern electronics displays.
Given a molecule, it is possible to calculate its phosphorescence when excited. However,
there is no direct method for finding molecules which maximize this property.
By applying P3 and other generic optimization methods we found some interesting
molecules for future analysis.

@@

A challenging task in machine learning is the training of large scale neural networks.
I have recently been in collaboration with an evolutionary biologist
who studies natural learning to develop better methods for training neural networks.
